### 2016-01-17 number_theory/hw/hw1.tex
homework and stuff

\item Suppose that $b\in\ZZ$.
\begin{enumerate}
\item If $4|b^{2}$, prove that $2|b$.
\begin{quote}
Assume that $4|b^{2}$ but $2\cancel{|}b$. Then $b = 2n + r$ for some $n$ and $r$ in $\ZZ$. We know
that $r\neq 0$, and that $0 < r < 2$. Therefore $r = 1$. If we square both sides, we get
\begin{align*}
b^{2} &= (2n+1)^{2}\\
&= 4n^{2}+4n+1\\
&= 4(n^{2} + n) + 1.
\end{align*}
Therefore $4\cancel{|}b$, since it has a remainder of 1.
\end{quote}

\end{enumerate}
\end{enumerate}
\end{document}

>>>>

\item Suppose that $b\in\ZZ$.
\begin{enumerate}
\item If $4|b^{2}$, prove that $2|b$.
\begin{quote}
Assume that $4|b^{2}$ but $2\cancel{|}b$. Then $b = 2n + r$ for some $n$ and $r$ in $\ZZ$. We know
that $r\neq 0$, and that $0 < r < 2$. Therefore $r = 1$. If we square both sides, we get
\begin{align*}
b^{2} &= (2n+1)^{2}\\
&= 4n^{2}+4n+1\\
&= 4(n^{2} + n) + 1.
\end{align*}
Therefore $4\cancel{|}b$, since it has a remainder of 1.
\end{quote}
\item If $9|b^{2}$, prove that $3|b$.
\begin{quote}
Assume that $9|b^{2}$, but $3\cancel{|}b$. Then $b=3n+r$ where $n$ and $r$ and in $\ZZ$, and
$0 < r < 3$. If we let $r=1$, then we have
\begin{align*}
b &= 3n + 1\\
b^{2} &= (3n+1)^{2}\\
&= 9n^{2} + 6n + 1\\
&= 3(3n^{2} + 2n) + 1.
\end{align*}
Therefore $3\cancel{|}b^{2}$, and since 3 is a factor of 9, $9\cancel{|}b^{2}$.
\end{quote}
$\triangle$
\end{enumerate}

\item Use the Euclidian Algorithm to calculate $gcd(1485,1745)$.
\begin{quote}
\begin{align*}
1745 &= 1485(1) + 260\\
1485 &= 260(5) + 185\\
260 &= 185(1) + 75\\
185 &= 75(2) + 35\\
75 &= 35(2) + 5\\
35 &= 5(7) + 0\\
\end{align*}
Therefore $gcd(1485,1745) = gcd(5,0) = 5$.
\end{quote}

\item Suppose that $a$ and $b$ are positive integers. Prove that $gcd(a,b) = a$ if and
only if $a|b$.
\begin{quote}
Assume that $gcd(a,b) = a$. Then $a$ is a divisor of both $a$ and $b$ by the definition of the $gcd$.
Therefore $a|b$.
\end{quote}
\end{enumerate}
\end{document}
